Convective Penetration Paper Outline

### 2021-05-08 notes/outline/outline.tex
small updates to outline tex file

\section{Intro \& Background}
\begin{itemize}
\item Observational \& Theoretical context: ``convective overshoot'' and the problems it relates to.
Include sources on e.g., 
\begin{itemize}
\item stellar Lithium abundances \citep[fig 4 of][]{pinsonneault_1997, dumont_etal_2021}, 
\item solar modeling problem \citep{basu_antia_2004, bahcall_etal_2005, zhang_li_2012, vinyoles_etal_2017, asplund_etal_2021},
\item helioseismology \citep[][]{christensen-dalsgaard_etal_2011},
\item stellar evolution \& remnants \citep{higgins_vink_2020}, 
\item stellar core convection overshoot \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021}, 
\item parameterizations \citep{shaviv_salpeter_1973, maeder1975, herwig2000}
\item``convective boundaries'' in MESA papers \citep{paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}. 
\item Other things?
\end{itemize}
\item Terminology of overshoot vs penetration.
\item Note that the state of the field has been reviewed many times by many authors \citep{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
We will do a brief review but these are additional resources.
\item Mention miscellaneous theoretical or semianalytical arguments or models \citep{roxburgh1965, roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998, marcus_etal_1983, zahn1991, hurlburt_etal_1994, rempel2004, canuto2011, viallet_etal_2015, rieutord2019, korre_etal_2019}.
\item Quick mention of penetration in the geophysical context \citep[including neat lab experiments like][]{deardorff_etal_1969}.
\item Briefly review simulations:
\begin{itemize}
\item ``Early'' simulations of e.g., plumes \citep{schmitt_etal_1984}.
\item Dynamical Cartesian simulations in both fully compressible and Boussinesq equation sets \citep{musman1968, moore_weiss_1973, hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, brummell_etal_2002, rogers_glatzmaier_2005, kapyla_etal_2007, tian_etal_2009, kitiashvili_etal_2016, lecoanet_etal_2016, kapyla_etal_2017, couston_etal_2017, toppaladoddi_wettlaufer_2018, kapyla2019, cai2020}.
\item Dynamical spherical geometry 2D or 3D simulations (fully compressible, anelastic, boussinesq, some solar-like, some not) \citep{browning_etal_2004, rogers_etal_2006, brun_etal_2017, pratt_etal_2017, dietrich_wicht_2018, higl_etal_2021}
\end{itemize}
\item Zahn's energetics arguments and the various times it has cropped up in the literature \citep{zahn1991, hurlburt_etal_1994, rempel2004, rogers_etal_2006}.
\item Simulations that have noticed that overshoot and/or penetration depends in some way on the flux \citep{singh_etal_1998, hotta2017, kapyla2019}.
\item State the conclusions of this work very clearly. 
\emph{The penetration depth depends on how steeply the radiative flux changes with depth near the radiative-convective boundary}.
Thus, the penetration depth depends on the slope of the radiative conductivity / the opacity near the boundaries of the CZ
We have designed two simple numerical setups which demonstrate this point.
\end{itemize}

>>>>

\section{Intro \& Background}
\begin{itemize}
\item The outline should be comprised of a few paragraphs, which basically say these things:
\begin{enumerate}
\item ``Convection is important in stars.''
\item ``Understanding convective boundaries is important (because of all of these observational and simulation and theoretical data points that show we kinda don't).'
\item People have thought about this problem theoretically in these ways.
\item We think the theoretical arguments of \citet{zahn1991}, who suggested that this is what convective penetration is, are really promising.
\item Here's what we do in this work.
\end{enumerate}
\item Observational \& Theoretical context: ``convective overshoot'' and the problems it relates to.
Include sources on e.g., 
\begin{itemize}
\item stellar Lithium abundances \citep[fig 4 of][]{pinsonneault_1997, dumont_etal_2021}, 
\item solar modeling problem \citep{basu_antia_2004, bahcall_etal_2005, zhang_li_2012, vinyoles_etal_2017, asplund_etal_2021},
\item helioseismology \citep[][]{christensen-dalsgaard_etal_2011},
\item black hole mass gap \citep{farmer_etal_2019}
\item stellar evolution \& remnants \citep{higgins_vink_2020}, 
\item stellar core convection overshoot \citep{claret_torres_2018, jermyn_etal_2018, viani_basu_2020, martinet_etal_2021}, 
\item parameterizations \citep{shaviv_salpeter_1973, maeder1975, herwig2000}
\item``convective boundaries'' in MESA papers \citep{paxton_etal_2011, paxton_etal_2013, paxton_etal_2018, paxton_etal_2019}. 
\item Other things?
\end{itemize}
\item Terminology of overshoot vs penetration.
\item Note that the state of the field has been reviewed many times by many authors \citep{marcus_etal_1983, zahn1991, browning_etal_2004, rogers_etal_2006, viallet_etal_2015, korre_etal_2019}.
We will do a brief review but these are additional resources.
\item Mention miscellaneous theoretical or semianalytical arguments or models \citep{roxburgh1965, roxburgh1978, roxburgh1989, roxburgh1992, roxburgh1998, marcus_etal_1983, zahn1991, hurlburt_etal_1994, rempel2004, canuto2011, viallet_etal_2015, rieutord2019, korre_etal_2019}.
\item Quick mention of penetration in the geophysical context \citep[including neat lab experiments like][]{deardorff_etal_1969}.
\item Briefly review simulations:
\begin{itemize}
\item ``Early'' simulations of e.g., plumes \citep{schmitt_etal_1984}.
\item Dynamical Cartesian simulations in both fully compressible and Boussinesq equation sets \citep{musman1968, moore_weiss_1973, hurlburt_etal_1986, hurlburt_etal_1994, singh_etal_1995, saikia_etal_2000, brummell_etal_2002, rogers_glatzmaier_2005, kapyla_etal_2007, tian_etal_2009, kitiashvili_etal_2016, lecoanet_etal_2016, kapyla_etal_2017, couston_etal_2017, toppaladoddi_wettlaufer_2018, kapyla2019, cai2020}.
\item Dynamical spherical geometry 2D or 3D simulations (fully compressible, anelastic, boussinesq, some solar-like, some not) \citep{browning_etal_2004, rogers_etal_2006, brun_etal_2017, pratt_etal_2017, dietrich_wicht_2018, higl_etal_2021}
\end{itemize}
\item Zahn's energetics arguments and the various times it has cropped up in the literature \citep{zahn1991, hurlburt_etal_1994, rempel2004, rogers_etal_2006}.
\item Simulations that have noticed that overshoot and/or penetration depends in some way on the flux \citep{singh_etal_1998, hotta2017, kapyla2019}.
\item State the conclusions of this work very clearly. 
\emph{The penetration depth depends on how steeply the radiative flux changes with depth near the radiative-convective boundary}.
Thus, the penetration depth depends on the slope of the radiative conductivity / the opacity near the boundaries of the CZ
We have designed two simple numerical setups which demonstrate this point.
\end{itemize}
